### 2020-01-27 report.tex
figures
alg

\documentclass{article}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmic}
\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage[T1,hyphens]{url}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{listings}
\lstset { %
    language=C++,
    %backgroundcolor=\color{black!5}, % set backgroundcolor
    basicstyle=\footnotesize,% basic font setting
}

@@

\section{Background}
We will assume the reader is familiar with SAT solving and the basics of the CDCL algorithm \cite{DBLP:series/faia/SilvaLM09}. We will use the notion of a trail to represent a sequence of literals corresponding to the current partial assignment. The literals appear on the trail in the order in which they were assigned. Associated with every literal on the trail is a decision level. Decision level 0 represents all literals which are implied by the formula itself and subsequent decisions start the beginning of a new decision level. When a literal is made true by unit propagation, the literal is given its decision level and a reason clause, where the reason clause is the clause that was made unit by propagation in order to imply this literal. Most modern solvers use the two-literal watch scheme to make unit propagation more efficient.

@@

@@

\begin{figure}
\begin{tabular}{|l|l|l|l|l|}
\hline
                 & cadical                     & cadical\_chrono & cadical\_trail & cadical\_trail\_enhanced \\ \hline
Instances Solved & 527                         & 515             & 520            & 524                      \\ \hline
Par-2 (x $10^6$s)& 3.220                  & 3.269      & 3.248     & 3.216               \\ \hline
                 & maple                       & maple\_chrono   & maple\_trail   & maple\_trail\_enhanced          \\ \hline
Instance Solved  & 458                         & 470             & 472            & 473                      \\ \hline
Par-2 (x $10^6$s)& 3.797 & 3.690      & 3.694     & 3.667               \\ \hline
\end{tabular}
\caption{Table of results}
\end{figure}
\begin{figure}\includegraphics[scale=0.8]{cactus_cadical.pdf}\caption{\small{Comparison of run times for versions of cadical. cadical is without chronological backtracking, cadical-chrono is with chronological backtracking, cadical-trail is with the first version of trail saving, cadical-trail-2levels-ahead is the trail saving with all enhancements added.}}\end{figure}
\begin{figure}\includegraphics[scale=0.8]{cactus_maple2.pdf}\caption{\small{Comparison of run times for versions of MapleSAT. maplelcmdist is from the 2017 SAT Competition, maplelecmdist-chrono is with chronological backtracking (2018 SAT Competition), maplelcmdist-trail is with the first version of trail saving, maplelcmdist-trail-enhanced is with trail saving and all enhancements added.}}\end{figure}
\iffalse
\begin{figure}\includegraphics[scale=0.8]{cactus_maple.pdf}\caption{\small{Comparison of run times for versions of MapleSAT. maplelcmdist is from the 2017 SAT Competition, maplelecmdist-chrono is with chronological backtracking (2018 SAT Competition), maplelcmdist-trail is with the first version of trail saving, maplelcmdist-chrono-dl is with chronological backtracking and duplicate learnts (2019 SAT Competition), maplelcmdist-trail-dl is with trail saving and duplicate learnts}}\end{figure}
\fi
\clearpage

>>>>

\documentclass{article}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[noend]{algcompatible}
\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage[T1,hyphens]{url}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{listings}
\lstset { %
    language=C++,
    %backgroundcolor=\color{black!5}, % set backgroundcolor
    basicstyle=\footnotesize,% basic font setting
}

@@

\section{Background}
We will assume the reader is familiar with SAT solving and the basics of the CDCL algorithm \cite{DBLP:series/faia/SilvaLM09}. We will use the notion of a trail to represent a sequence of literals corresponding to the current partial assignment. The literals appear on the trail in the order in which they were assigned. Associated with every literal on the trail is a decision level. Decision level 0 represents all literals which are implied by the formula itself and subsequent decisions start the beginning of a new decision level. When a literal is made true by unit propagation, the literal is given its decision level and a reason clause, where the reason clause is the clause that was made unit by propagation in order to imply this literal. Most modern solvers use the two-literal watch scheme to make unit propagation more efficient, where each clause is watched by two non-false literals. When a watcher for a clause becomes false, a replacement is searched for in the clause. If no such replacement exists

@@

	\begin{algorithm}
  	\caption{propagate()}
	\begin{algorithmic}[1]
	\WHILE{queue not empty}
	\STATE $l := $ next literal on queue
	\\BEGIN CODE TO ADD FOR TRAIL SAVING
	\IF{trail saving turned on}
		\IF{val(top of trail cache) $=$ true}
			\WHILE{trail cache not empty}
				\STATE{move top of trail cache to next literal}
				\STATE{let tc $=$ top of trail cache}
				\IF{reason(tc) is null}
					\STATE{break}
				\ELSIF{val(tc) $=$ false}
					\STATE{return conflict with reason(tc)}
				\ELSIF{val(tc) $=$ unassigned}
					\STATE{enqueue tc with reason reason(tc)}
				\ENDIF
			\ENDWHILE
		\ENDIF
	\ENDIF
	\\END CODE TO ADD FOR TRAIL SAVING
  	\FOR{each clause $c \in $ watchlist($\neg l$)}
		\FOR{each literal $x \in c$}
			\IF{$val($x$) \neq$ false and x is not already a watcher of c}
				\STATE let $x$ be a watcher of $c$ and add $c$ to watchlist($\neg x$)
				\STATE break
			\ENDIF
		\ENDFOR
		\IF{no new watcher was found}
			\IF{other watcher $x_2$ of $c = $ false}
				\STATE return c as conflict
			\ELSIF{other watcher $x_2$ of $c$ is unassigned}
				\STATE enqueue $x_2$
			\ENDIF
		\ENDIF
	\ENDFOR
	\ENDWHILE
	\end{algorithmic}
	\end{algorithm}
\clearpage

@@

\begin{figure}
\begin{tabular}{|l|l|l|l|l|}
\hline
                 & cadical                     & cadical\_chrono & cadical\_trail & cadical\_trail\_enhanced \\ \hline
Instances Solved & 527                         & 515             & 520            & 524                      \\ \hline
Par-2 (x $10^6$s)& 3.220                  & 3.269      & 3.248     & 3.216               \\ \hline
                 & maple                       & maple\_chrono   & maple\_trail   & maple\_trail\_enhanced          \\ \hline
Instance Solved  & 458                         & 470             & 472            & 473                      \\ \hline
Par-2 (x $10^6$s)& 3.797 & 3.690      & 3.694     & 3.667               \\ \hline
\end{tabular}
\caption{Table of results}
\end{figure}
\begin{figure}\includegraphics[scale=0.8]{cactus_cadical.pdf}\caption{\small{Comparison of run times for versions of cadical. cadical is without chronological backtracking, cadical-chrono is with chronological backtracking, cadical-trail is with the first version of trail saving, cadical-trail-2levels-ahead is the trail saving with all enhancements added.}}\end{figure}
\begin{figure}\includegraphics[scale=0.8]{cactus_maple2.pdf}\caption{\small{Comparison of run times for versions of MapleSAT. maplelcmdist is from the 2017 SAT Competition, maplelecmdist-chrono is with chronological backtracking (2018 SAT Competition), maplelcmdist-trail is with the first version of trail saving, maplelcmdist-trail-enhanced is with trail saving and all enhancements added.}}\end{figure}
\begin{figure}\includegraphics[scale=0.8]{test.pdf}\caption{}\end{figure}
\begin{figure}\includegraphics[scale=0.8]{test2.pdf}\caption{}\end{figure}
\iffalse
\begin{figure}\includegraphics[scale=0.8]{cactus_maple.pdf}\caption{\small{Comparison of run times for versions of MapleSAT. maplelcmdist is from the 2017 SAT Competition, maplelecmdist-chrono is with chronological backtracking (2018 SAT Competition), maplelcmdist-trail is with the first version of trail saving, maplelcmdist-chrono-dl is with chronological backtracking and duplicate learnts (2019 SAT Competition), maplelcmdist-trail-dl is with trail saving and duplicate learnts}}\end{figure}
\fi
\clearpage
